Exploring the Validity Range of PLL Analytical Models

### 2025-05-22 CaseStudies/Example3_2_LimitsoftheTheorySoFar/Report/article/article.qmd
Studying.

# Gerar gráfico
plt.figure(figsize=(8, 5))
plt.plot(t_out * 1e6, y_out, label='Resposta ao Degrau')
plt.plot(t_out * 1e6, u, linestyle=':', color='black', label='Entrada Degrau')
plt.axhline(final_value + tol, color='red', linestyle='--', linewidth=0.8, label='Faixa ±1%')
plt.axhline(final_value - tol, color='red', linestyle='--', linewidth=0.8)
plt.axvline(ts_graphical * 1e6, color='green', linestyle='--', linewidth=1.2, label=f'Settling time (gráfico): {ts_graphical*1e6:.2f} ns')
plt.xlabel('Time [ns]')
plt.ylabel('Phase [rad]')
plt.title('Resposta ao Degrau com Tempo de Acomodação (99%)')
plt.grid(True)
plt.legend()
plt.tight_layout()
plt.show()
```

@@

## TODO: Analyze control voltage to verify if cycle slipping occurs if $\Delta\omega>\Delta\omega_m$

@@

Com a intenção de se realizar testes para verificar a ocorrência de cycle slipping, estima-se a mínima frequência do sinal de referência. A ratio often quoted as being safe is 10:1 for $\omega_r/\omega_n$, dessa forma, a mínima frequência segura para o sinal de referência é dado por $f_r=$ `{python} format(f_r_safe)`Hz. A mínima frequência permitida, é dada por:

@@

ou seja, a mínima frequência de referência é $f_r\ge$ `{python} format(f_r_max)`Hz. Dessa forma, como é desejada uma PLL operando com frequência de referência $f_r=$ `{python} format(f_r)`Hz e frequência de saída `{python} format(f_o)`Hz, o sistema projetado deve operar corretamente.

>>>>

# Gerar gráfico
plt.figure(figsize=(8, 5))
plt.plot(t_out * 1e6, y_out, label='Step Response')
plt.plot(t_out * 1e6, u, linestyle=':', color='black', label='Step')
plt.axhline(final_value + tol, color='red', linestyle='--', linewidth=0.8, label='±1% Tolerance')
plt.axhline(final_value - tol, color='red', linestyle='--', linewidth=0.8)
plt.axvline(ts_graphical * 1e6, color='green', linestyle='--', linewidth=1.2, label=f'Graphical settling time: {ts_graphical*1e6:.2f} us')
plt.xlabel('Time [us]')
plt.ylabel('Phase [rad]')
plt.title('Step Response with Settling Time (99%)')
plt.grid(True)
plt.legend()
plt.tight_layout()
plt.show()
```

@@

## Cycle slipping analyzing

@@

With the intention of conducting tests to verify the occurrence of cycle slipping, the minimum frequency of the reference signal is estimated. A ratio often quoted as being safe is 10:1 for $\omega_r/\omega_n$; thus, the minimum safe frequency for the reference signal is given by $f_r=$ `{python} format(f_r_safe)`Hz. The minimum allowed frequency is given by:

@@

That is, the minimum reference frequency is $f_r\ge$ `{python} format(f_r_max)`Hz. Therefore, since a PLL operating with a reference frequency of $f_r=$ `{python} format(f_r)`Hz and an output frequency of `{python} format(f_o)`Hz is desired, the designed system must operate correctly.

Using the Simulink software, a testbench was prepared to verify the settling time of the PLL. With the previously calculated parameters and using the maximum step frequency value, the resulting curve can be seen in [Fig. @fig-max-step-response]. It can be observed that the step is applied at the instant of 1 ms, as the system is already properly stabilized at that moment. As predicted, cycle slipping does not occur; however, unlike what was calculated, the settling time of this signal is $9.196\;\mu\text{s}$.

![System response to the maximum step frequency](../images/max_step_frequency_response.jpg){#fig-max-step-response}

```{python}
#| echo: false
cycle_slip_step_lin = 3*step_m_lin

Moreover, contrary to what was previously predicted, for cycle slipping to occur, the step frequency must be approximately $\Delta f=$ `{python} format(cycle_slip_step_lin)`Hz. The system's response to this signal can be seen in [Fig. @fig-cycle-slip-response].

![System response with cycle slip](../images/step_frequency_response_cycle_slip.jpg){#fig-cycle-slip-response}
